Actuator line modeling of vertical-axis turbines

### 2016-05-13 paper.tex
Past tense

NACA 0021 coefficients were used for both turbines, despite the fact that the
UNH-RVAT is constructed from NACA 0020 foils, as a NACA 0020 dataset is not
available---it is assumed the small difference in foil thickness is negligible.
Since pitching moment data were only available at limited Reynolds numbers, two
datasets were used: The lowest for $Re_c \leq 3.6 \times 10^5$ and highest $Re_c
\geq 6.8 \times 10^5$. For each actuator line element, blade chord Reynolds
number is computed based on the sampled inflow velocity, and the static
coefficients are then interpolated linearly within the database.

>>>>

NACA 0021 coefficients were used for both turbines, despite the fact that the
UNH-RVAT is constructed from NACA 0020 foils, as a NACA 0020 dataset was not
available---it is assumed the small difference in foil thickness is negligible.
Since pitching moment data were only available at limited Reynolds numbers, two
datasets were used: The lowest for $Re_c \leq 3.6 \times 10^5$ and highest $Re_c
\geq 6.8 \times 10^5$. For each actuator line element, blade chord Reynolds
number is computed based on the sampled inflow velocity, and the static
coefficients are then interpolated linearly within the database.
